Visualize atlantisom

### 2020-05-11 Visualize_atlantisom.Rmd
add single functions
to do next text

@@

```{r depgraph}

@@

>>>>

[`drake`](https://docs.ropensci.org/drake/)

@@

This is all the functions in `atlantisom`:

```{r depgraph, message=FALSE}

@@

This is just the `om_init` wrapper function:

```{r depgraphominit}

depominit <- funDependencies("package:atlantisom", "om_init")
plot(depominit)

While these map dependencies between functions, it would be nice to see what output of atlantis goes into atlantisom and what atlantisom outputs into SS3.
